---
title: "Processing Widening Data"
author: "Natalia Mushegian"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(sf)
library(osmextract)
library(tmap)
library(tictoc)
library(tigris)
```

Reading and processing data from NC DOT Received May 13th, 2024 from Meredith Vick (msvick@ncdot.gov) - "Please see attached.  Our construction unit indicated we can’t create the formats requested but did add in a couple more columns that were shown on the STIP list (counties, route numbers).  The output of our contract admin software shows each county and route in a line by itself, so there will be multiple lines for each contract."

```{r}
all_projects <- read_excel('../data/Completed Project List_withOSMids_noquo.xlsm')
widening <- all_projects %>% filter(grepl("WIDENING",`Contract Description`))
```


```{r}
contracts <- widening %>% group_by(`Contract Number`) %>% summarise(county = first(County), location = first(`Location Description`), description = first(`Contract Description`), routettype = first(`Route Type`), routenum = first(`Route Number`), date = max(`Acceptance Date`), nchunks = n()) %>% arrange(date) #not totally correct route number, which is somehow different for each of the chunks

#widening <- widening %>% mutate(id_list = split(OSMids, ' '))
```

Example: SR-1003 (CAMDEN RD) FROM EAST OF OAKLAND AVE TO NORTH OF SR-1007 (OWEN DR).

This link shows it was actually a multiphase project: https://www.fayettevillenc.gov/Home/Components/News/News/6761/397?arch=1

```{r}
# getting osm data from a download instead of pulling from web
#"This file was last modified 17 hours ago and contains all OSM data up to 2024-07-01T20:21:29Z"

#worked - 2354915 obs (more roads than we need), tags in extra_tags
#nc <- oe_read('north-carolina-latest.osm.pbf')

#worked - 447122 obs, correct tags as columns (incl. oneway)
tic('read osm data')
nc <- oe_read('../data/north-carolina-latest.osm.pbf', extra_tags = c('oneway', 'maxspeed'), query="SELECT *
              FROM 'lines'
              WHERE highway IN ('motorway', 'primary', 'secondary', 'tertiary', 'trunk', 'residential')")#,
              #force_vectortranslate = TRUE)
toc() #31 sec

nc <- nc  %>% st_transform(crs=st_crs(32616)) # needed for the inner buffer in km

#write_sf(nc, 'northcarolinaroads.shp') # saving the shp in case it's faster to read than the .pbf

# now there's a north-carolina-latest.gpkg, can read that to skip the conversion but still need other options? check this out later but aborting this attempt for now
#nc_gpkg <- oe_read('north-carolina-latest.gpkg')
```

```{r filter_osm}
#cleaning up my OSM id sins
split_ids <- widening %>% separate(OSMids, into=paste0("id",1:81), sep = ' ') %>% # hard coded to the max number of segments in one of my widenings - 81
  filter(id1 != 'unclear' & id1 != "can't" & id1 != "Greene")

pivoted <- split_ids %>% pivot_longer(cols=starts_with('id'), values_to = "osm_id") %>% filter(!is.na(osm_id)) # drop a huge number of NAs from contracts that had only a few segments

wide_roads <- nc %>% filter(osm_id %in% pivoted$osm_id)

# below for reading from file rather than running the code
#write_sf(wide_roads, 'expandedroads.shp') # saving the shp to avoid loading and filtering all NC roads again - to be updated when I add more roads. NOTE: not all info in other_tags preserved
#wide_roads <- read_sf('expandedroads.shp')
```

```{r keep contract info}
wide_roads <- left_join(wide_roads, (pivoted %>% select(`Contract Number`, `Contract Description`, `Acceptance Date`, osm_id)), by='osm_id')
wide_contracts <- wide_roads %>% group_by(`Contract Number`) %>% summarise(name = first(name),
                                                         description = first(`Contract Description`),
                                                         maxspeed = first(maxspeed),
                                                         highway = first(highway),
                                                         oneway=first(oneway),
                                                         date = first(`Acceptance Date`),
                                                         OSMids = list(osm_id))
```



```{r show_em}
tmap_mode("view")
tm_shape(wide_contracts) + tm_lines(col='red', id='name', legend.col.show = FALSE)
```

Toss borders, cut big projects, cut by number of lanes? or a state classification (use state roads database)

1. Remove anything within X distance of a border (thinking 20 or 30 miles)
2. Remove anything classified as 'motorway'
3. Remove any combined segment longer than 10 miles

I'm running this all on *wide_contracts* right now because it's easier to make sure I'm treating all the segments of one contract together, but will eventually want to switch back to wide_roads probably so that I keep the matching OSMids. or maybe i go back and extract them via overlap or something?

```{r}
nc_counties <- counties("NC") %>% st_transform(crs=st_crs(32616))
nc_poly <- states() %>% filter(GEOID == 37) %>% st_transform(crs=st_crs(32616))
nc_inner <- st_buffer(nc_poly, -30000)
#plot(nc_inner)

length_threshold <- 15000 #-> need a histogram of segment lengths
units(length_threshold) <- "m"

# 38 contracts originally pre filtering
shortlist <- wide_contracts %>% filter(highway != "motorway") %>% # goes down to 36 after this
  st_filter(nc_inner, .predicate = st_within) %>% # now 21 with 30km buffer, this cuts some coastal stuff that probably doesn't need to be cut
  mutate(contract_length = st_length(.)) %>%
  filter(contract_length < length_threshold) %>% # now 19 for contracts less than 15 km
  filter(date > as.Date("2019-01-01")) %>% # now 15
  filter(date < as.Date("2022-01-01")) # now 10
  
tm_shape(shortlist) + tm_lines(col='date', id='name', palette = "RdBu")

#write_sf(shortlist, "expansions_shortlist_20240805.shp")

#instead of cutting stuff out, just adding additional labels. highway label already in there, no need to add
expanded_tagged <- wide_contracts %>% mutate(inner_state_30km = as.numeric(st_within(wide_contracts, nc_inner)) > 0) %>% # add a label for things in the inner region (not 30 km)
  mutate(contract_length = st_length(.)) %>% # add a length label
  select(-OSMids) %>% # dropping these because they don't write well to shapefile and i'd rather re-read them later
  st_transform(crs = st_crs(4326)) # to match the routes data

write_sf(expanded_tagged, "../data/all_expansions_ncdot_data.shp") # use this file in label_od

```


```{r}
buffer_30km <- shortlist %>% st_buffer(30*1000)
buffer_60km <- shortlist %>% st_buffer(60*1000)

tmap_mode('view')
tm_shape(buffer_60km) + tm_polygons(col='blue') + tm_shape(buffer_30km) + tm_polygons() + tm_shape(wide_contracts) + tm_lines() + tm_shape(shortlist) + tm_lines(col='red')
```




Shortlist and comments:

"Battleground Avenue" - https://www.ncdot.gov/projects/us-220-widening-greensboro/Documents/december-2018-public-comment-summary.pdf, http://grra.org/wp-content/uploads/2018/12/Fall-2018-1.pdf, may be too big (filter out trunk too?)

"Camden Road" - press release: https://www.fayettevillenc.gov/Home/Components/News/News/6761/ this shows that while the acceptance date is 2019, half of the project opened by 2017
more construction more recently, https://www.nc-eminent-domain.com/latest-projects/camden-road-widening/     this seems related: https://www.ncdot.gov/projects/fayetteville-outer-loop/Pages/project-highlights.aspx

"River Road"                
"Strickland Bridge Road"   
NA                          
"Ramsey Street"             
"Lakewood Drive"            
"East 4th Avenue"           
"Lick Creek Church Road"    
"Coach Deal Road"           
